Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-05-20 manuscript.tex
Final fix [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355518964

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/9f26f343eb6707bf20436bc0f58fa1c34dc74c00/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/9f26f343eb6707bf20436bc0f58fa1c34dc74c00}{jojoelfe/deco\_lace\_template\_matching\_manuscript@9f26f34}
on May 20, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/e94f17b00fe53a7b703becda30c7a1b1503e6e7e/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/e94f17b00fe53a7b703becda30c7a1b1503e6e7e}{jojoelfe/deco\_lace\_template\_matching\_manuscript@e94f17b}
on May 20, 2022.
